### 2016-07-11 capability-machine.tex
removed readCondition from entry cond

\newcommand{\readCond}[1]{\plainfun{readCondition}(#1)}
\newcommand{\writeCond}[1]{\plainfun{writeCondition}(#1)}
\newcommand{\execCond}[1]{\plainfun{executeCondition}(#1)}
\newcommand{\entryCond}[1]{\plainfun{entryCondition}(#1)}

@@

\subsection*{Semantics}
Assume a $\decode$ function that decodes integer to instructions:
\begin{align*}
\decode &:\ints \rightarrow \Instrs
\end{align*}
Assume an $\encodePerm$ function that encodes a permission as an integer:
\begin{align*}
\encodePerm &: \Perms \rightarrow \ints
\end{align*}
\begin{align*}
  \Phi & \rightarrow \sem{\decode(\memreg(\pcreg))}(\Phi) & &                                   
                                                              \arraycolsep=0pt
                                                              \begin{array}{l}
                                                                \text{if $\memreg(\pcreg) = \stdcap$}\\
                                                                \quad\text{and $\start \leq \addr < \addrend$}\\
                                                                \quad\text{and $\perm \in \{ \exec,\rwx \}$ }
                                                              \end{array}\\
\Phi & \rightarrow \failed                                 & & \text{otherwise}
\end{align*}
It is assumed that address 0 is used for I/O, so whatever resides in location 0 after an execution can be seen as a result. As we will see in the semantics, it is assumed that the initial process starts with a readwrite capability for this location.
\begin{align*}
  \executeAllowed{\perm} &=
                           \begin{cases}
                             \true & \text{if } \perm \in \{ \rwx, \exec, \entry \} \\
                             \false & \text{otherwise}
                           \end{cases} \\
  \readAllowed{\perm} &=
                           \begin{cases}
                             \true & \text{if } \perm \in \{ \rwx, \exec, \readwrite, \readonly \} \\
                             \false & \text{otherwise}
                           \end{cases} \\
  \writeAllowed{\perm} &=
                           \begin{cases}
                             \true & \text{if } \perm \in \{ \rwx, \readwrite\} \\
                             \false & \text{otherwise}
                           \end{cases} \\
  \updatePcPerm{(\perm,\start,\addrend,\addr)} &=
                                     \begin{cases}
                                       (\exec,\start,\addrend,\addr) & \text{if $\perm = \entry$}
                                       (\perm,\start,\addrend,\addr) & \text{otherwise} \\

@@

                                                              \quad\text{and $r_1\neq \pcreg$}\\
                                                              \quad\text{for $i \in \{1,2\}$}\\

@@

\begin{align*}
  \readCond{n,W,\start,\addrend} =        & \;\exists r \in \RegionName \ldotp \\
                                          & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nsubeq[n-1] \iota_{\start',\addrend'} \\ & \\
  \writeCond{n,W,\start,\addrend} =       & \; \exists r \in \RegionName \ldotp \\
                                          & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nequal[n-1] \iota_{\start',\addrend'} \\ & \\
  \execCond{n,W,\start,\addrend,\perm} =  & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                          & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
                                          & \; \qquad \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(W') \\ & \\
  \entryCond{n,W,\start,\addrend,\addr} = & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                          & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(W') \land \\
                                          & \; \quad \readCond{n',W',\addrend,\addr}
\end{align*}

>>>>

\newcommand{\readCond}[1]{\plainfun{readCondition}(#1)}
\newcommand{\writeCond}[1]{\plainfun{readWriteCondition}(#1)}
\newcommand{\execCond}[1]{\plainfun{executeCondition}(#1)}
\newcommand{\entryCond}[1]{\plainfun{entryCondition}(#1)}

@@

\subsection*{Semantics}
Assume a $\decode$ function that decodes integer to instructions:
\decode &:\ints \rightarrow \Instrs
Assume an $\encodePerm$ function that encodes a permission as an integer:
\encodePerm &: \Perms \rightarrow \ints
  \Phi & \rightarrow \sem{\decode(\memreg(\pcreg))}(\Phi) & &                                   
                                                                \quad\text{and $\start \leq \addr < \addrend$}\\
                                                                \quad\text{and $\perm \in \{ \exec,\rwx \}$ }
\Phi & \rightarrow \failed                                 & & \text{otherwise}
It is assumed that address 0 is used for I/O, so whatever resides in location 0 after an execution can be seen as a result. As we will see in the semantics, it is assumed that the initial process starts with a readwrite capability for this location.
  \executeAllowed{\perm} &=
                             \true & \text{if } \perm \in \{ \rwx, \exec, \entry \} \\
  \readAllowed{\perm} &=
                             \true & \text{if } \perm \in \{ \rwx, \exec, \readwrite, \readonly \} \\
  \writeAllowed{\perm} &=
                             \true & \text{if } \perm \in \{ \rwx, \readwrite\} \\
  \updatePcPerm{(\perm,\start,\addrend,\addr)} &=
                                       (\exec,\start,\addrend,\addr) & \text{if $\perm = \entry$}\\
                                       (\perm,\start,\addrend,\addr) & \text{otherwise} 

@@

                                                              \quad\text{and for $i \in \{1,2\}$}\\

@@

\begin{align*}
  \readCond{n,W,\start,\addrend} =        & \;\exists r \in \RegionName \ldotp \\
                                          & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nsubeq[n-1] \iota_{\start',\addrend'} \\ & \\
  \writeCond{n,W,\start,\addrend} =       & \; \exists r \in \RegionName \ldotp \\
                                          & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp W(r) \nequal[n-1] \iota_{\start',\addrend'} \\ & \\
  \execCond{n,W,\start,\addrend,\perm} =  & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                          & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
                                          & \; \qquad \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(W') \\ & \\
  \entryCond{n,W,\start,\addrend,\addr} = & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
                                          & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(W') \land \\
\end{align*}
